Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-12-09 manuscript/manuscript.tex
re-enable inline figs

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/data-processing_model-architecture}
%           \caption{Diagram of the data processing, model fitting, tuning, and prediction pipeline.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_validation}
%           \caption{Out of sample test set performance for salinity, turbidity, and temperature models respectively. Hatching indicates the location of 80\% of the data points.}
%     \end{center}
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.8\textwidth,keepaspectratio]{figures/_importance_all}
%           \caption{Random Forest importance plot for salinity, temperature, and turbidity models. Note that all features may not be present in all models if they were dropped as a result of recursive feature elimination.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/_seasonality}
%           \caption{Seasonal Random Forest prediction results for temperature and salinity.}
%     \end{center}    
% \end{figure}

@@

% \begin{figure}[ht!]
%     \begin{center}
%           \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_rf-vs-cbofs}
%           \caption{Comparison between Random Forest salinity prediction results and a CBOFS snapshot for Sept, 4, 2022.}
%     \end{center}    
% \end{figure}

@@

\clearpage

\section*{Figure Captions}

\begin{description}
    \item Figure 1: Diagram of the data processing, model fitting, tuning, and prediction pipeline.
    \item Figure 2: Out of sample test set performance for salinity, turbidity, and temperature models respectively. Hatching indicates the location of 80\% of the data points.
    \item Figure 3: Random Forest importance plot for salinity, temperature, and turbidity models. Note that all features may not be present in all models if they were dropped as a result of recursive feature elimination.
    \item Figure 4: Seasonal Random Forest prediction results for temperature and salinity.
    \item Figure 5: Comparison between Random Forest salinity prediction results and a CBOFS snapshot for Sept, 4, 2022.
\end{description}

>>>>

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/data-processing_model-architecture}
          \caption{Diagram of the data processing, model fitting, tuning, and prediction pipeline.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_validation}
          \caption{Out of sample test set performance for salinity, turbidity, and temperature models respectively. Hatching indicates the location of 80\% of the data points.}
    \end{center}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.8\textwidth,keepaspectratio]{figures/_importance_all.png}
          \caption{Random Forest importance plot for salinity, temperature, and turbidity models. Note that all features may not be present in all models if they were dropped as a result of recursive feature elimination.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.7\textwidth,keepaspectratio]{figures/_seasonality}
          \caption{Seasonal Random Forest prediction results for temperature and salinity.}
    \end{center}    
\end{figure}

@@

\begin{figure}[ht!]
    \begin{center}
          \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/_rf-vs-cbofs}
          \caption{Comparison between Random Forest salinity prediction results and a CBOFS snapshot for Sept, 4, 2022.}
    \end{center}    
\end{figure}

@@
